---
title: "Exam2_Schleich_Fabian"
author: "Fabian Schleich"
date: "2024-12-01"
output: 
 pdf_document: 
  default
fontsize: 5pt
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## R Markdown

#requirments of the exam are: 
Data: 
done-read in data from line 26 on in 
done-*NOTE:* One of the files contains random ',' as a numeric separator, which will force the entire column to be read as a character class. You will need to replace the ',' separator with '.' to properly convert the column to numeric.
done-where is the time varaible??
done -dont filter tourq data this way, some peaks have same value and are filtered out atm --> add super tiny bit of unique random data before filtering??? test on CTM15.txt, we accept that one out of 144 peaks are not captured
done -calculate torque minima and maxima and plot them, use splus2R package(peaks() function) to identify them

-Read in and asign usefull names (FIle: A_BID_CTM01; "folder name" "_" "filename before the .txt"); take "before"; or "after" from file name, Info in file: speed: x

Plotting:
done-x axis: time(min) with a bit of padding/starting before 0, then 2500, 5000, 7500 (plotting everything up to 10.000)
done-plot speed, angle, torque as "names" underneath plot
done -y axis: value -130 to 200, with xaxis lines at 100, 0 and -100


-Plot angle, speed and torque for 16 data sets in 3 diffrent colors value vs time (min) --> facit wrap or for loop?
-Plot header (file name but not the -txt), exercise: before and after (added to folder) and speed: x

Finish:
-knit them as pdf together
-Name pdf "Exam2_Schleich_Fabian"



#Load liberies/install
```{r 1}
#install.packages("tidyverse")
#install.packages("splus2R")
library(tidyverse)
library(splus2R)
library(tibble)

```



#load data and info
```{r, data}
#Step1
#load path first
dirty_path <- "C:/Users/fabisc/OneDrive - Karolinska Institutet/Documents/Courses/Intermediate R/Schleich_R_project_asigment/Day8and9_Exam2/data"
#list all files 
all_dirty_files <- list.files(path = dirty_path, recursive = T , pattern = ".txt", full.names = T)
#?list.files


all_dirty_files_names <- paste0(str_extract(all_dirty_files, "([A-Z]_)?R2|([A-Z]_)?BID"),'_', gsub('.txt', '', basename(all_dirty_files)))
#?basename
#?gsub
#all_dirty_files_names

#Step2 +3
#col names to rename the columns
cool_names <- c("Torque", "Speed", "Angle" )

#make a list, then make it characters, then remove the ".", 
#then revert to numeric and then add the names
#then add the time column
#used for peaks input
all_cleaned_files_list <- all_dirty_files %>%
  map(~ read.table(.x, skip = 26, header = FALSE)) %>%
  map(~ .x %>% 
        mutate_all(as.character) %>%                   #strings
        mutate_all(~ str_replace_all(., ",", ".")) %>% #remove "."
        mutate_all(as.numeric)                         #Convert back to numeric
       )%>%
  map(. %>% purrr::set_names(cool_names)) %>%          #names of column set
  set_names(all_dirty_files_names) %>%                 #names of dataframes set
  map(~ .x %>% mutate(time = 1:nrow(.x)) )         #time column lenght nrow

#then use pivot to make longer, will be used for plotting
all_cleaned_files_list_long <- all_cleaned_files_list %>%
    map(~ .x %>% pivot_longer(cols = c(Torque, Speed, Angle), 
               names_to = "variable", 
               values_to = "value"))

#map(all_cleaned_files_list, head) 
#?map
#?read.table
#?set_names


```

#local min and maxima
```{r, splus2R package(peaks() function)}
#pulls torque values only
#makes logical values from peak value for positive
all_cleaned_files_list_torque_max <- all_cleaned_files_list %>%
  map(~ .x %>% pull(Torque)) %>%
  map(~ peaks(.x, span=280, strict=F, endbehavior = 1))
  
#make num values out of them, then filter for positive values and round them
all_cleaned_files_list_torque_max_value <- map2(
  all_cleaned_files_list,             # List of data frames
  all_cleaned_files_list_torque_max,  # List of logical vectors
  ~ .x %>% filter(.y == TRUE))        # Filter rows for TRUE
#read in data and filter it
all_cleaned_files_list_torque_max_value_filtered <- all_cleaned_files_list_torque_max_value %>%
  map(~ .x %>% filter(Torque > 30)) %>%
  map(~ .x %>% distinct(Torque, .keep_all = T)) %>%
  map(~ .x %>% mutate(Torque = round(Torque, 2)))
  

#makes logical values from peak value for negative
all_cleaned_files_list_torque_min <- all_cleaned_files_list %>%
  map(~ .x %>% mutate(Torque = -Torque))
#then use this dataframe as before
all_cleaned_files_list_torque_min_a <- all_cleaned_files_list_torque_min %>%
  map(~ .x %>% pull(Torque)) %>%
  map(~ .x %>% peaks(span=400, strict=F, endbehavior = 1))

#make num values out of them, then filter for positive values and round them
all_cleaned_files_list_torque_min_value <- map2(
  all_cleaned_files_list,             # List of data frames
  all_cleaned_files_list_torque_min_a,  # List of logical vectors
  ~ .x %>% filter(.y == TRUE))        # Filter rows for TRUE
#read in data and filter it
all_cleaned_files_list_torque_min_value_filtered <- all_cleaned_files_list_torque_min_value %>%
  map(~ .x %>% filter(Torque < -50)) %>%          #filter low values out
  map(~ .x %>% distinct(Torque, .keep_all = T)) %>%  #filter non-unique out
  map(~ .x %>% mutate(Torque = round(Torque, 2)))   #round 

```

#additonal data 
```{r, additonal data}
# Extract the speed info
speed <- all_dirty_files %>% 
  map(read.table, nrows = 1, header = T, col.names = 'info') %>% # read in the files
  map(. %>% tibble::rownames_to_column(var = 'id')) %>% # assign row names to column  
  map(. %>% unite('note', id:info, sep = ': ', remove = T)) %>% # unite to columns into one 
  set_names(all_dirty_files_names) # define the names for each df in a list
# Print head of all dfs in the list
#map(speed, head)

# Create additional info - here you don't need to do anything. Rather try to understand how code works
info <- data.frame(path = all_dirty_files,
                   file_names = all_dirty_files_names) %>% 
  mutate(condition = ifelse(grepl('BID',.$path), 'Exercise: Before', 'Exercise: After')) %>% 
  select(file_names, condition)

# print info
#print(info)

```




#data is read in time to start plotting
```{r, plot}
#plot all 16 plots
plots_all_clean_plots <- lapply(1:length(speed), function(i) {
  
  ggplot(data = all_cleaned_files_list_long[[i]], aes(time, value, color = variable)) + # define main ggplot 
    geom_path() + # line is ugly so i used path
    geom_point(data = all_cleaned_files_list_torque_max_value_filtered[[i]], 
               aes(x = time, y = Torque), inherit.aes = FALSE) + #max
    geom_point(data = all_cleaned_files_list_torque_min_value_filtered[[i]], 
               aes(x = time, y = Torque), inherit.aes = FALSE) + #min
    labs(col = '', y = 'Value', x = 'Time(min)',
         title = paste('File:', names(speed)[i]),
         subtitle = paste(info$condition[info$file_names == names(speed)[i]],'\n',
                          str_to_title(speed[[i]]$note)))+
    geom_text(data = all_cleaned_files_list_torque_max_value_filtered[[i]], 
            aes(x = time, y = Torque, label = Torque), nudge_y  = 15, size = 3, inherit.aes = FALSE)+
    geom_text(data = all_cleaned_files_list_torque_min_value_filtered[[i]], 
             aes(x = time, y = Torque, label = Torque), nudge_y  = -15, size = 3, inherit.aes = FALSE)+
      theme_bw()+
    theme(
     legend.title = element_blank(), 
     panel.grid.major = element_line(),
     panel.grid.minor = element_blank(),
     legend.position = "bottom",
  )
})


# print third figure
plots_all_clean_plots

```



```{r}
# Save the plots in the single .pdf file
pdf(file = paste0(dirty_path, '/Schleich_Fabian-Alexander_Exam2_results_figs.pdf'))
map(plots_all_clean_plots, function(plot) print(plot))
dev.off()
```
*THE END :)*


#And something to remember:
What I think it really means is: I'm a teacher. I am a teacher. I teach all the time, as you do and as all of you do-whether we know it or not, whether we take responsibility for it or not. I hold nothing back because I want to see that light go off. I like to see the children say, 'I never thought of that before.' And I think, 'I've got them!'- Maya Angelou

Thank you for making me think, "I never thought of that before." Alen.


