---
title: "Exam2_Schleich_Fabian"
author: "Fabian Schleich"
date: "2024-12-01"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## R Markdown

#requirments of the exam are: 
Data: 
done-read in data from line 26 on in 
done-*NOTE:* One of the files contains random ',' as a numeric separator, which will force the entire column to be read as a character class. You will need to replace the ',' separator with '.' to properly convert the column to numeric.
done-where is the time varaible??
done -dont filter tourq data this way, some peaks have same value and are filtered out atm --> add super tiny bit of unique random data before filtering??? test on CTM15.txt, we accept that one out of 144 peaks are not captured
done -calculate torque minima and maxima and plot them, use splus2R package(peaks() function) to identify them

-Read in and asign usefull names (FIle: A_BID_CTM01; "folder name" "_" "filename before the .txt"); take "before"; or "after" from file name, Info in file: speed: x

Plotting:
done-x axis: time(min) with a bit of padding/starting before 0, then 2500, 5000, 7500 (plotting everything up to 10.000)
done-plot speed, angle, torque as "names" underneath plot
done -y axis: value -130 to 200, with xaxis lines at 100, 0 and -100


-Plot angle, speed and torque for 16 data sets in 3 diffrent colors value vs time (min) --> facit wrap or for loop?
-Plot header (file name but not the -txt), exercise: before and after (added to folder) and speed: x

Finish:
-knit them as pdf together
-Name pdf "Exam2_Schleich_Fabian"



#Load liberies/install
```{r 1}
#install.packages("tidyverse")
#install.packages("splus2R")
library(tidyverse)
library(splus2R)
library(tibble)

```



#load data and info into seperate onjectes
```{r, data}
#load data into object to then start tiding it up
dirty_file <- ("C:/Users/fabisc/OneDrive - Karolinska Institutet/Documents/Courses/Intermediate R/Schleich_R_project_asigment/Day8and9_Exam2/data/A_R2/CTM02.txt")

#makes it string readable
dirty_txt_file <- read_lines(dirty_file)
#replaces , with . (ended up beeing a porblem later on)
slightly_cleaner_txt_file <- str_replace_all(dirty_txt_file, ",", ".")
#generate temp file to read_tsv can start reading it again
temp_file <- tempfile(fileext = ".txt")
write_lines(slightly_cleaner_txt_file, temp_file)

#col names to rename the columns
cool_names <- c("Torque", "Speed", "Angle" )
#read only the data portion 
dirty_data <- read_tsv(temp_file, skip = 26, col_names = cool_names, col_types = cols(angle = col_double(), speed = col_double(), torque = col_double()))

#when not replacing the , by . this was used to find the error
#problems(dirty_data) #one datapoint uses . instead of , 

#count number of events
time <- (1:nrow(dirty_data))

#read only the information portion
dirty_info <- read_tsv(dirty_file, n_max = 1, col_names = c("text", "Speed"), skip =1) ##supposed to use speed column as part of title


#?read_tsv
#add the events/time to the dirty data, making it a bit less dirty
slightly_less_dirty_data <- cbind(time, dirty_data)
#slightly_less_dirty_data <- cbind(slightly_less_dirty_data, dirty_info)

#make it long data
long_slightly_less_dirty_data <- slightly_less_dirty_data %>%
  pivot_longer(cols = c(Angle, Speed, Torque), 
               names_to = "variable", 
               values_to = "value")
```

#local min and maxima
```{r, splus2R package(peaks() function)}
#?peaks()
x <- slightly_less_dirty_data

#find positive maxima and make them a vector
z <- slightly_less_dirty_data %>%
  peaks(span=200, strict=F, endbehavior = 1) %>%
  pull(Torque)

#use logical vector, make num values out of them, then filter for positive values and round them
zz <- slightly_less_dirty_data%>%
  filter(z == TRUE)%>%
  filter(Torque > 30)%>%
  distinct(Torque, .keep_all = T)%>%
  mutate(Torque = round(Torque, 2))


#?filter
#same but for negative inflextion points
y <- slightly_less_dirty_data %>%
  mutate(Torque = -Torque) %>%
  peaks(span=460, strict=F, endbehavior = 1) %>%
  pull(Torque)


#do the same but for neg values
yy<-slightly_less_dirty_data%>%
  filter(y == TRUE)%>%
  filter(Torque < -60)%>%
  distinct(Torque, .keep_all = T)%>%
  mutate(Torque = round(Torque, 2))


```


#data is read in time to start plotting
```{r, plot}
#raw plot using geom path 
ggplot(data = long_slightly_less_dirty_data, aes(time, value, color = variable))+
  geom_path()+  #geom line looked diffrent then reference
  geom_point(data = zz, aes(x = time, y = Torque), inherit.aes = FALSE)+
  geom_point(data = yy, aes(x = time, y = Torque), inherit.aes = FALSE)+
  geom_text(data = zz, aes(x = time, y = Torque, label = Torque), nudge_y  = 15, size = 3, inherit.aes = FALSE)+
   geom_text(data = yy, aes(x = time, y = Torque, label = Torque), nudge_y  = -15, size = 3, inherit.aes = FALSE)+
  labs(
    title ="File: A_BID_CTM01", 
    subtitle = "Exercise: Before; Speed: 30",
    x = "time(sec)",
    y = "Value") +
  theme_bw()+
  theme(
    legend.title = element_blank(), 
    panel.grid.major = element_line(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom",
  )

#?geom_text
```

