*
---
title: "Exam3_Schleich_new"
author: "Fabian Schleich"
date: "2024-11-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#requirments of the exam are: 
Data: 
done-read in data from line 26 on in 
done-*NOTE:* One of the files contains random ',' as a numeric separator, which will force the entire column to be read as a character class. You will need to replace the ',' separator with '.' to properly convert the column to numeric.

-Read in and asign usefull names (FIle: A_BID_CTM01; "folder name" "_" "filename before the .txt"); take "before"; or "after" from file name, Info in file: speed: x

-where is the time varaible??
-calculate torque minima and maxima and plot them, use splus2R package(peaks() function) to identify them

Plotting:
-Plot angle, speed and torque for 16 data sets in 3 diffrent colors value vs time (min) --> facit wrap or for loop?
-Plot header (file name but not the -txt), exercise: before and after (added to folder) and speed: x
-y axis: value -130 to 200, with xaxis lines at 100, 0 and -100
-x axis: time(min) with a bit of padding/starting before 0, then 2500, 5000, 7500 (plotting everything up to 10.000)
-plot speed, angle, torque as "names" underneath plot

Finish:
-knit them as pdf together
-Name it "Exam2_Schleich_Fabian"



#Load liberies/install
```{r 1}
#install.packages("tidyverse")
#install.packages("splus2R")
library(tidyverse)
library(splus2R)
```



#load data and info into seperate onjectes
```{r}
#load data into object to then start tiding it up
dirty_file <- ("C:/Users/fabisc/OneDrive - Karolinska Institutet/Documents/Courses/Intermediate R/Schleich_R_project_asigment/Day8and9_Exam2/data/Before_A_BID/CTM01.txt")

#makes it string readable
dirty_txt_file <- read_lines(dirty_file)
#replaces , with . (ended up beeing a porblem later on)
slightly_cleaner_txt_file <- str_replace_all(dirty_txt_file, ",", ".")
#generate temp file to read_tsv can start reading it again
temp_file <- tempfile(fileext = ".txt")
write_lines(slightly_cleaner_txt_file, temp_file)

#col names to rename the columns
cool_names <- c("angle", "speed", "torque")
#read only the data portion 
dirty_data <- read_tsv(temp_file, skip = 26, col_names = cool_names, col_types = cols(angle = col_double(), speed = col_double(), torque = col_double()))

#when not replacing the , by . this was used to find the error
#problems(dirty_data) #one datapoint uses . instead of , 


#read only the information portion
dirty_info <- read_tsv(dirty_file , n_max = 1)
```
#data is read in time to start plotting
```{r}
ggplot(data = dirty_data)


```

